Constraining the Interiors of Asteroids Through Close Encounters

### 2022-02-10 summaries/21-11/21-11.tex
Pulled perigee probes up to 25

\shorttitle{Asteroid project summary}
\shortauthors{Dinsmore and de Wit}

@@

\title{Asteroid project summary}

@@

\begin{abstract}

Abstract. 
\end{abstract}

>>>>

\shorttitle{Constraining the Interiors of Asteroids Through Close Encounters}
\shortauthors{Dinsmore and de Wit}

@@

\title{Constraining the Interiors of Asteroids Through Close Encounters}

@@

\begin{abstract}
We investigate the degree to which asteroid interior density distributions can be extracted from rotational velocity data gathered during a close encounter. We derive the equations of motion for an asteroid's orientation and angular velocity during a close encounter to arbitrary precision and use them to generate synthetic rotational velocity data for a representative asteroid on a close Earth flyby. We re-extract the properties of the asteroid from this synthetic data and confirm the fit's accuracy. We investigate the dependence of the best fit uncertainty on asteroid moment of inertia, observational precision and cadence, the flyby's orbital parameters, the initial spin pole direction, the quantity of near-pericenter data, and the oblateness of the central body. Finally, we discuss the degeneracy between the parameters that can be extracted from flyby data and the actual density distribution and propose four models to construct a representative density distribution.
\end{abstract}
